\speculake: Hiding Malware in Speculative Execution

### 2018-08-07 paper/figures.tex
figures.tex
figure fixes

\newcommand{\FigSpectreOne}{
\begin{figure}[t]
    \centering
    \includegraphics[width=0.9\linewidth]{figures/spectre_1_training.png}
    \caption{\textbf{Speculative buffer overflow warm-up}\,---\, %
    The direct branch predictor must
    be trained to expect that a branch will go a specific way before speculative
    buffer overflows can be used. We varied the number of times a branch was trained
    to be taken and observed the fraction of times we achieved a speculative buffer overflow
    execution immediately after (measured by observing if a speculatively-loaded value was present
    in cache avgeraged over 20,000 trials). We find that a branch must be trained in a
    direction at least 400 times before it can start to be used in a speculative buffer overflow.}
    \label{fig:spectre-one}
\end{figure}
}

@@

\newcommand{\FigSpecMeasureNP}{
\begin{figure*}[t]
     \centering
        \includegraphics[width=0.9\textwidth]{figures/Speculative_measurements_no-parity.png}
        \caption{\textbf{Speculative limits}\,---\, %
    To find the number of instructions we can execute speculatively, we placed a speculative load
    after an increasing number of instructions, and measured the fraction of times the load
    was subsequently in cache. We find that we can execute up to 220 instructions speculatively,
    which corresponds with the size of the CPU's reorder buffer (ROB). However, more complex instructions
    have stricter constraints, generally corresponding to the number of $\mu$-ops that an instruction
    comprises.}
    \label{fig:spec-capacity-np}
\end{figure*}
}

>>>>

\newcommand{\FigSpectreOne}{
\begin{figure}[t]
    \centering
    \includegraphics[width=0.9\linewidth]{figures/spectre_1_training.png}
    \caption{\textbf{Speculative buffer overflow warm-up}\,---\, %
    The direct branch predictor must
    be trained to expect that a branch will go a specific way before speculative
    buffer overflows can be used. We varied the number of times a branch was trained
    to be taken and observed the fraction of times we achieved a speculative buffer overflow
    execution immediately after (measured by observing if a speculatively-loaded value was present
    in cache avgeraged over 20,000 trials). We find that a branch must be trained in a
    direction hundreds of times before it can start to be used in a speculative buffer overflow.}
    \label{fig:spectre-one}
\end{figure}
}

@@

\newcommand{\FigSpecMeasureNP}{
\begin{figure*}[t]
     \centering
        \includegraphics[width=0.9\textwidth]{figures/Speculative_measurements_no-parity.png}
        \caption{\textbf{Speculative limits}\,---\, %
    To find the number of instructions we can execute speculatively, we placed a speculative load
    after an increasing number of instructions, and measured the fraction of times the load
    was subsequently in cache. However, more complex instructions
    have stricter constraints, generally corresponding to the number of $\mu$-ops that an instruction
    comprises. We find that we can execute up to 220 instructions 
    speculatively, which corresponds with the size of the CPU's reorder buffer (ROB). We measure 
    the ROB size by timing two cache accesses with a variable number of 
    instructions between them. The step in cycles around 220 instructions indicates that the 
    second cache access was pushed out of the ROB defining an upper limit on size.  }
    \label{fig:spec-capacity-np}
\end{figure*}
}
